Borel regularity for ODEs and Thimble Integrals

### 2024-02-07 exp-resurgence.tex
Start writing up proof of lem:picard-power
Also, change ODE setting to match regular singular Volterra paper.

@@

The central goal of this paper is to explain, from this perspective, why Borel summation works well for the two kinds of problems exemplified in Section~\ref{intro:summation}.
\begin{enumerate}
\item Solving a linear ODE of single level~$1$ \cite[Section 2.1]{EcalleIII}\cite[Section~5.2.2.1]{diverg-resurg-iii}. One example is Equation~\eqref{eqn:bessel-rescaled-1}. The general example is the equation $\mathcal{P} \Phi = 0$ given by a differential operator of the form
\[ \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_{d-1}(z^{-1})\,\partial_z^{d-1} \big], \]
where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_0, \ldots, R_{d-1}$ are holomorphic functions in some disk $|z|>A$ around infinity. We'll restrict our attention to the case where the roots of $P$ are simple (see Section \ref{borel_reg-ODE}).

@@

%We can use the Laplace transform to convert $\mathcal{P}$ into a family of integral operators $\hat{\mathcal{P}}_\upsilon$ parameterized by the point $\zeta = \upsilon$ on the position domain.
\color{Maroon}
\begin{theorem}\label{thm:borel_reg_ODE}
Choose a root $-\alpha$ of $P$. Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and doesn't touch any other root of $P(-\zeta)$. Equation~\eqref{eqn:standard ODE} has a unique solution $\Psi_\alpha$ in the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$ from Section~\textcolor{orange}{[figure out where to put definition]}. That solution is Borel regular.
\end{theorem}
\textcolor{violet}{If you prefer to work in the analytic world, you can use this result to prove the existence and Borel summability of special formal transmonomial solutions.}
\begin{corollary}\label{cor:borel_reg_ODE}
For each root $-\alpha$ of $P$, Equation~\eqref{eqn:standard ODE} has a formal solution in the transmonomial space $e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$, which is unique up to scaling. That solution is Borel summable, and its Borel sum is a constant multiple of $\Psi_\alpha$.
\end{corollary}
\textcolor{violet}{On the other hand, if you prefer to work in the formal world, you can use Theorem~\ref{thm:borel_reg_ODE} to show that the Poincar\'{e} solutions are Borel summable. See Section~\ref{sec:new-summability-proof}.}
\textcolor{violet}{[In another section, do the ``mirror image'' argument. Use the Poincar\'{e} algorithm to construct a formal transmonomial solution in the classical way. Use the Ramis index theorem to show that it's Gevrey-$1$, and then then use our existence and uniqueness result for regular singular Volterra equations to show that it's not only Gevrey-$1$, but in fact Borel summable.]}
%%The formal solution whose existence is shown in Corollary~\ref{cor:borel_reg_ODE} is the Poincar\'{e} solution.
%%\begin{corollary}
%%\textcolor{orange}{[The Poincar\'{e} solution is Borel summable.]}
%%\end{corollary}
\color{black}
\textcolor{Violet}{[This is sort of a mirror image of the Ramis index theorem?]}
\begin{theorem}[see Theorem \ref{thm2-dim}]\label{thm2}
The formal frame of solutions $\tilde{\Psi}_j$ is Borel summable \textcolor{orange}{[summability is the strongest part of the result]} and its Borel sum is proportional to $\Psi_j$. In fact, $\Psi_j$ is a Borel regular solution of \eqref{eqn:standard ODE}. \textcolor{orange}{[Alternate statement: look in Sauzin or Delabaere to get uniqueness of formal solution.]} \textcolor{orange}{[Split into theorem, which shows existence of Borel regular frame, and corollary, which shows that this implies a certain frame of formal solutions is Borel-summable and sums to actual solutions.]}
\end{theorem}
%
We summarize the main steps of the proof of Theorem~\ref{thm:borel_reg_ODE} and Corollary~\ref{cor:borel_reg_ODE} (the rigorous proofs are given in Section~\ref{borel_reg-ODE}). On the right-hand side of the diagram, we have the formal solution $\series{\Psi }_\alpha\in e^{-\alpha z}z^{-\tau_\alpha}\C\llbracket z^{-1}\rrbracket$ and its Borel transform $\series{\psi}_\alpha$. %Then, the theory of $1$-summability allows us to draw the ``square'' with corners $\hat{\psi}_j$ and its Laplace transform $\hat{\Psi}_j$.

@@

\section{Proof of main results}\label{sec:proof_main_results}
\subsection{Borel regularity for ODEs}\label{borel_reg-ODE}
\textcolor{orange}{[Make sure this matches regular singular Volterra paper!]} Recall the setting from Section~\ref{borel-reg:explanatory-power}: let $\mathcal{P}$ be a linear differential operator\footnote{ We follow Delabaere, rather than \'Ecalle, in only going on up to degree $d-1$; see \cite[Footnote~1 in Section 5.2.2.1]{diverg-resurg-iii}}
\begin{equation}
\mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_{d-1}(z^{-1})\,\partial_z^{d-1} \big],
\end{equation}

\begin{itemize}
\item $P$ is a monic degree-$d$ polynomial with simple zeros; \footnote{Unlike \'Ecalle, we don't require all the roots of $P$ to be non-zero, because  we can translate in the position domain.}
\item $Q$ is a degree-$(d-1)$ polynomial and $Q(-\alpha)\neq 0$ for all zeros $\alpha$;
\item $R_0(z^{-1}), \ldots, R_{d-1}(z^{-1})$ are holomorphic in some disk $|z| > A$ around $z = \infty$.
\end{itemize}

For every zeros $\alpha$, let $\Omega_\alpha\subset B$ be a simply connected open set that touches but doesn't contain $\zeta = \alpha$. We also assume:
\begin{itemize}
\item The set $\Omega_\alpha$ is star-shaped around $\zeta = \alpha$. In other words, for any $a \in \Omega_\alpha$, a straight path from $\zeta = \alpha$ to $a$ stays in $\Omega_\alpha$. Since $\Omega_\alpha$ doesn't contain $\zeta = \alpha$, we'll always leave that starting point out of the path.
\item The set $\Omega_\alpha$ does not contain the tubular neighborhood of the other critical points, as shown in Figure \ref{Fig:domain}. \textcolor{orange}{[In ``Regular singular Volterra,'' we assume that $\Omega_\alpha$ doesn't touch any other critical point (that is, doesn't contain any other critical point in its closure). Under the star-shaped assumption, I think that implies avoiding tubular neighborhoods of the shadow rays.]}
\end{itemize}

\begin{figure}
\center
\begin{tikzpicture}
\newcommand{\spill}{4}
\fill[violet!20, bezier bounding box, path fading=radial edge]
  (-\spill, -\spill) (\spill, \spill)
  (0, 0) -- (160:\spill)
  arc (160:112:\spill) -- (112:2) .. controls (112:1.7) and (103:1.7) .. (103:2) -- (103:\spill)
  arc (103:50:\spill) -- (50:2.6) .. controls (50:2.2) and (43:2.2) .. (43:2.6) -- (43:\spill)
  arc (43:-52:\spill) -- (-52:2.3) .. controls (-52:2) and (-60:2) .. (-60:2.3) -- (-60:\spill)
  arc (-60:-130:\spill) -- (0, 0);
\fill[violet] circle (0.7mm) node[anchor=195, outer sep=1mm] {$\zeta = \alpha$};
\node[anchor=north west, outer sep=1mm] at (46.5:2.46) {$\zeta=\beta$};
\foreach \p in {(107.5:1.95), (46.5:2.46), (-56:2.24)} {
  \fill \p circle (0.7mm);
}
\end{tikzpicture}
\caption{The domain $\Omega_\alpha$}\label{Fig:domain}
\end{figure}
\subsubsection{Proof of main results}
\color{Maroon}
\begin{theorem}[restatement of \ref{thm:borel_reg_ODE}]
Choose a root $-\alpha$ of $P$. Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and doesn't touch any other root of $P(-\zeta)$. Equation~\eqref{eqn:standard ODE} has a unique solution $\Psi_\alpha$ in \textcolor{magenta}{[the appropriate affine subspace of]} the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$ from Section~\textcolor{orange}{[figure out where to put definition]}. That solution is Borel regular.
\end{theorem}
The key to our proof is recasting Equation~\eqref{eqn:standard ODE} as an integral equation in the position domain. This integral equation belongs to a well-behaved class of regular singular Volterra equations, which we study in~\cite{reg-sing-volterra}. In particular, it can be solved using Picard iteration, which refines an initial guess toward the unique solution in its basin of attraction. We'll use the guess $\frac{1}{\Gamma(\tau_\alpha)} \zeta^{\tau_\alpha - 1}$ to find a solution $\psi_\alpha$ with the same singularity at $\zeta_\alpha = 0$ \cite[Theorem~4]{reg-sing-volterra}.
%%\begin{theorem}(Theorem~4 from \cite{reg-sing-volterra})
%%\textcolor{orange}{[\ldots]}
%%\end{theorem}

For the Borel regularity part of the proof, we need to make a connection between the analytic and formal worlds. To do this in the position domain, we again use Picard iteration. \textcolor{orange}{[Does this generalize Delabaere's argument? If so, mention that.]}
\begin{lemma}
\textcolor{orange}{[The solution $\zeta_\alpha^{1 - \tau_\alpha} \psi_\alpha$ (or something) extends holomorphically over $\zeta = \alpha$.]}
\end{lemma}
\begin{proof}
\textcolor{orange}{[\ldots]}
\end{proof}
\begin{lemma}
The equation $\hat{\mathcal{P}}_\alpha \series{\psi}_\alpha = 0$ has a unique formal solution $\series{\psi}_\alpha$ in the affine subspace
\[ \frac{\zeta_\alpha^{\tau_\alpha-1}}{\Gamma(\tau_\alpha)} + \zeta_\alpha^{\tau_\alpha} \C\llbracket \zeta_\alpha \rrbracket \]
of the space $\zeta_\alpha^{\tau_\alpha - 1} \C\llbracket \zeta_\alpha \rrbracket$.
\end{lemma}
\begin{proof}
\textcolor{orange}{[Argument of Loday-Richaud\ldots]}
\end{proof}
\begin{proof}
Let $\hat{\mathcal{P}}_\alpha$ be the Volterra operator defined in Section~4.5 of \cite{reg-sing-volterra}. Take any holomorphic function $\phi$ on $\Omega_\alpha$ with a well-defined Laplace transform $\Phi = \laplace_{\zeta,\alpha}^{\theta} \phi$ \textcolor{magenta}{[choose $\theta$]}. Lemma~2 of \cite{reg-sing-volterra} shows that $\hat{\mathcal{P}}_\alpha \phi = 0$ if and only if $\mathcal{P}\Phi = 0$ \textcolor{magenta}{[the lemma only states one direction; change it before publication to state both directions]}.

By Theorem~4 of \cite{reg-sing-volterra}, the equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace
\[ \frac{\zeta^{\tau_\alpha-1}}{\Gamma(\tau_\alpha)} + \singexpalg{\tau_\alpha}(\Omega_\alpha) \]
of the space $\singexpalg{\tau_\alpha-1}(\Omega_\alpha)$. The same is true on any smaller sector created by shaving a sector off each edge of $\Omega_\alpha$. It follows, by the results of Section~\ref{sec:reg-decay} \textcolor{magenta}{[the domain $\Omega_\alpha$ needs to be a sector for this]}, that the equation $\mathcal{P}\Psi_\alpha = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace
\[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \]
of the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$.

>>>>

% regular singular volterra operator
\newcommand{\volterra}{\mathcal{V}}
\newcommand{\hardpart}{\mathcal{V}_0}
\newcommand{\softpart}{\mathcal{V}_\star}
%%\newcommand{\kerwhole}{k}
\newcommand{\hardker}{k_0}
%%\newcommand{\softker}{k_\star}
\newcommand{\solwhole}{f}
\newcommand{\solproto}{f_0}
\newcommand{\solptb}{f_\star}
%%\newcommand{\roots}{\mathfrak{B}}

@@

The central goal of this paper is to explain, from this perspective, why Borel summation works well for the two kinds of problems exemplified in Section~\ref{intro:summation}.
\begin{enumerate}
\item Solving a linear ODE of single level~$1$ \cite[Section 2.1]{EcalleIII}\cite[Section~5.2.2.1]{diverg-resurg-iii}. One example is Equation~\eqref{eqn:bessel-rescaled-1}. \textcolor{magenta}{The general example [not anymore---we've restricted]} is the equation $\mathcal{P} \Phi = 0$ given by a differential operator of the form
\[ \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2} R(z^{-1}), \]
where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial that's non-zero at every root of $P$, and $R(z^{-1})$ is holomorphic in some disk $|z| > A$ around $z = \infty$. We'll restrict our attention to the case where the roots of $P$ are simple (see Section \ref{borel_reg-ODE}).

@@

%We can use the Laplace transform to convert $\mathcal{P}$ into a family of integral operators $\hat{\mathcal{P}}_\upsilon$ parameterized by the point $\zeta = \upsilon$ on the position domain.
\color{Maroon}
\begin{theorem}\label{thm:borel_reg_ODE}
Choose a root $-\alpha$ of $P$. Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and doesn't touch any other root of $P(-\zeta)$. Equation~\eqref{eqn:standard ODE} has a unique solution $\Psi_\alpha$ in the affine subspace
\[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \]
of the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$ from Section~\textcolor{orange}{[figure out where to put definition]}. That solution is Borel regular.
\end{theorem}
\textcolor{violet}{If you prefer to work in the analytic world, you can use this result to prove the existence and Borel summability of special formal transmonomial solutions.}
\begin{corollary}\label{cor:borel_reg_ODE}
For each root $-\alpha$ of $P$, Equation~\eqref{eqn:standard ODE} has a formal solution in the transmonomial space $e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$, which is unique up to scaling. That solution is Borel summable, and its Borel sum is a constant multiple of $\Psi_\alpha$.
\end{corollary}
\textcolor{violet}{On the other hand, if you prefer to work in the formal world, you can use Theorem~\ref{thm:borel_reg_ODE} to show that the Poincar\'{e} solutions are Borel summable. See Section~\ref{sec:new-summability-proof}.}
\textcolor{violet}{[In another section, do the ``mirror image'' argument. Use the Poincar\'{e} algorithm to construct a formal transmonomial solution in the classical way. Use the Ramis index theorem to show that it's Gevrey-$1$, and then then use our existence and uniqueness result for regular singular Volterra equations to show that it's not only Gevrey-$1$, but in fact Borel summable.]}
%%The formal solution whose existence is shown in Corollary~\ref{cor:borel_reg_ODE} is the Poincar\'{e} solution.
%%\begin{corollary}
%%\textcolor{orange}{[The Poincar\'{e} solution is Borel summable.]}
%%\end{corollary}
\color{black}
\textcolor{Violet}{[This is sort of a mirror image of the Ramis index theorem?]}
\begin{theorem}[see Theorem \ref{thm2-dim}]\label{thm2}
The formal frame of solutions $\tilde{\Psi}_j$ is Borel summable \textcolor{orange}{[summability is the strongest part of the result]} and its Borel sum is proportional to $\Psi_j$. In fact, $\Psi_j$ is a Borel regular solution of \eqref{eqn:standard ODE}. \textcolor{orange}{[Alternate statement: look in Sauzin or Delabaere to get uniqueness of formal solution.]} \textcolor{orange}{[Split into theorem, which shows existence of Borel regular frame, and corollary, which shows that this implies a certain frame of formal solutions is Borel-summable and sums to actual solutions.]}
\end{theorem}
%
We summarize the main steps of the proof of Theorem~\ref{thm:borel_reg_ODE} and Corollary~\ref{cor:borel_reg_ODE} (the rigorous proofs are given in Section~\ref{borel_reg-ODE}). On the right-hand side of the diagram, we have the formal solution $\series{\Psi }_\alpha\in e^{-\alpha z}z^{-\tau_\alpha}\C\llbracket z^{-1}\rrbracket$ and its Borel transform $\series{\psi}_\alpha$. %Then, the theory of $1$-summability allows us to draw the ``square'' with corners $\hat{\psi}_j$ and its Laplace transform $\hat{\Psi}_j$.

@@

\section{Proof of main results}\label{sec:proof_main_results}
\subsection{Borel regularity for ODEs}\label{borel_reg-ODE}
\subsubsection{Proof of main results}
Let's recall the setting from Section~\ref{borel-reg:explanatory-power}. Let $\mathcal{P}$ be a linear differential operator of the form
%%\footnote{We follow Delabaere, rather than \'{E}calle, in only going on up to degree $d-1$; see \cite[Footnote~1 in Section 5.2.2.1]{diverg-resurg-iii}}
\[ \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2} R(z^{-1}), \]
where
\begin{enumerate}
\item[$\bullet$] $P$ is a monic degree-$d$ polynomial whose roots are all simple; 
\item[$\bullet$] $Q$ is a degree-$(d-1)$ polynomial that's non-zero at every root of $P$;
\item[$\bullet$] $R(z^{-1})$ is holomorphic in some disk $|z| > A$ around $z = \infty$. In particular, the power series
\[ R(z^{-1}) = \sum_{j=0}^\infty R_j z^{-j} \]
converges in the region $|z| > A$.
\end{enumerate}
%%For each root $-\alpha$ of $P$, choose an open sector $\Omega_\alpha \subset \C$ that has $\zeta = \alpha$ at its tip, doesn't touch any other root of $P(-\zeta)$, and has an opening angle of $\pi$ or less.
\textcolor{orange}{[Discuss terminology, like in \tt{reg-sing-volterra}?]}
%%%\begin{itemize}
%%%\item The set $\Omega_\alpha$ is star-shaped around $\zeta = \alpha$. In other words, for any $a \in \Omega_\alpha$, a straight path from $\zeta = \alpha$ to $a$ stays in $\Omega_\alpha$. Since $\Omega_\alpha$ doesn't contain $\zeta = \alpha$, we'll always leave that starting point out of the path.
%%%\item The set $\Omega_\alpha$ does not contain the tubular neighborhood of the other critical points, as shown in Figure \ref{Fig:domain}. \textcolor{orange}{[In ``Regular singular Volterra,'' we assume that $\Omega_\alpha$ doesn't touch any other critical point (that is, doesn't contain any other critical point in its closure). Under the star-shaped assumption, I think that implies avoiding tubular neighborhoods of the shadow rays.]}
%%%\end{itemize}

\begin{figure}
\center
\begin{tikzpicture}
\newcommand{\spill}{4}
\fill[violet!20, bezier bounding box, path fading=radial edge]
  (-\spill, -\spill) (\spill, \spill)
  (0, 0) -- (160:\spill)
  arc (160:112:\spill) -- (112:2) .. controls (112:1.7) and (103:1.7) .. (103:2) -- (103:\spill)
  arc (103:50:\spill) -- (50:2.6) .. controls (50:2.2) and (43:2.2) .. (43:2.6) -- (43:\spill)
  arc (43:-52:\spill) -- (-52:2.3) .. controls (-52:2) and (-60:2) .. (-60:2.3) -- (-60:\spill)
  arc (-60:-130:\spill) -- (0, 0);
\fill[violet] circle (0.7mm) node[anchor=195, outer sep=1mm] {$\zeta = \alpha$};
\node[anchor=north west, outer sep=1mm] at (46.5:2.46) {$\zeta=\beta$};
\foreach \p in {(107.5:1.95), (46.5:2.46), (-56:2.24)} {
  \fill \p circle (0.7mm);
}
\end{tikzpicture}
\caption{The domain $\Omega_\alpha$ \textcolor{orange}{[Revise to show asector]}}\label{Fig:domain}
\end{figure}
\color{Maroon}
\begin{theorem}[restatement of \ref{thm:borel_reg_ODE}]
Choose a root $-\alpha$ of $P$. Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and doesn't touch any other root of $P(-\zeta)$. Equation~\eqref{eqn:standard ODE} has a unique solution $\Psi_\alpha$ in the affine subspace
\[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \]
of the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$ from Section~\textcolor{orange}{[figure out where to put definition]}. That solution is Borel regular.
\end{theorem}
The key to our proof is recasting Equation~\eqref{eqn:standard ODE} as an integral equation in the position domain. This integral equation belongs to a well-behaved class of regular singular Volterra equations, which we study in~\cite{reg-sing-volterra}. In particular, it can be solved using Picard iteration, which refines an initial guess toward the unique solution in its basin of attraction. We'll use \textcolor{magenta}{the guess $\frac{1}{\Gamma(\tau_\alpha)} \zeta^{\tau_\alpha - 1}$ [actually, use prototype solution instead]} to find a solution $\psi_\alpha$ with the same singularity at $\zeta_\alpha = 0$.
%%\begin{theorem}[Theorem~4 from \cite{reg-sing-volterra}]\label{thm:sing-soln}
%%The equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace
%%\[ \zeta_\alpha^{\tau_\alpha-1} + \singexpalg{\tau_\alpha}(\Omega_\alpha) \]
of the space $\singexpalg{\tau_\alpha-1}(\Omega_\alpha)$.
%%\end{theorem}

For the Borel regularity part of the proof, we need to make a connection between the analytic and formal worlds. To do this in the position domain, we again use Picard iteration. \textcolor{orange}{[This does seem to generalize Delabaere's argument! We should confirm and mention that.]}
\begin{lemma}\label{lem:picard-power}
In Theorem~4 of \cite{reg-sing-volterra}, the solution $\psi_\alpha$ can be expressed as the sum of a power series in $\zeta_\alpha^{\tau_\alpha - 1} \C\{\zeta_\alpha\}$.
%%can be expressed as a convergent power series of the form
%%\[ c_1 \zeta_\alpha^{\tau_\alpha - 1} + c_2 \zeta_\alpha^{\tau_\alpha} + c_3 \zeta_\alpha^{\tau_\alpha + 1} + c_4 \zeta_\alpha^{\tau_\alpha + 2} + \ldots. \]
\end{lemma}
\begin{proof}
%%Theorem~\ref{thm:sing-soln} is a corollary of Theorem~\ref{thm:general_volterra} of \cite{reg-sing-volterra}.
The ring of formal power series $\C\{\zeta_\alpha\}$ is isomorphic to the ring of germs of holomorphic functions at $\zeta = \alpha$. This isomorphism identifies the analytic and formal versions of the integration operator $\partial^{-1}_{\zeta, \alpha}$. In the argument that follows, we'll only distinguish the analytic and formal interpretations of $\C\{\zeta_\alpha\}$ when we need to.

For convenience, let $p = P(-\zeta)$ and $q = Q(-\zeta)$. In \cite{reg-sing-volterra}, to prove Theorem~4, we rewrite the equation $\hat{\mathcal{P}}_\alpha \solwhole = 0$ as a regular singular Volterra equation $\solwhole = \volterra^\alpha \solwhole$ that satisfies the conditions of Theorem~3. The operator $\volterra^\alpha$ is the sum of the ``prototypical'' part
%%\[ \hardpart^\alpha = -\tfrac{1}{P(-\zeta)} \circ \partial^{-1}_{\zeta, \alpha} \circ Q(-\zeta) \]
\[ \hardpart^\alpha = -\tfrac{1}{p} \circ \partial^{-1}_{\zeta, \alpha} \circ q \]
and the perturbation
%%\[ \softpart^\alpha = \tfrac{1}{P(-\zeta)} \circ \partial^{-2}_{\zeta, \alpha} \circ R(\partial^{-1}_{\zeta, \alpha}) \]
\[ \softpart^\alpha = \tfrac{1}{p} \circ \partial^{-2}_{\zeta, \alpha} \circ R(\partial^{-1}_{\zeta, \alpha}). \]

Let's run through the proof of Theorem~3, specialized to the case we consider in Theorem~4. First, picking an arbitrary point $b \in \Omega_\alpha$, we show that the {\em prototype solution}
\[ \solproto(a) = \frac{1}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right) \]
satisfies the equation $\solproto = \hardpart^\alpha \solproto$. We then look for a perturbation $\solptb$ that makes $\solwhole = \solproto + \solptb$ a solution of the Volterra equation we're trying to solve. This is equivalent to solving the inhomogeneous equation
\begin{equation}\label{eqn:inhomog-volterra}
\solptb = \softpart^\alpha \solproto + \volterra^\alpha \solptb
\end{equation}

The central idea of the proof is to show that $\solproto$ lies in $\singexpalg{\tau_\alpha - 1}(\Omega_\alpha)$, that $\softpart^\alpha$ maps $\singexpalg{\tau_\alpha - 1}(\Omega_\alpha)$ into $\singexpalg{\tau_\alpha}(\Omega_\alpha)$ \textcolor{orange}{[check]}, and that $\volterra^\alpha$ is a contraction of $\singexp{\tau_\alpha}{\Lambda}(\Omega_\alpha)$ when $\Lambda$ is large enough. It follows, by the Banach fixed point theorem, equation~\eqref{eqn:inhomog-volterra} has a unique solution $\solptb$ in $\singexp{\tau_\alpha}{\Lambda}(\Omega_\alpha)$. More explicitly, we can solve equation~\eqref{eqn:inhomog-volterra} by Picard iteration. Starting with any initial guess $\solptb^{(0)} \in \singexp{\tau_\alpha}{\Lambda}(\Omega_\alpha)$ and defining
\begin{align*}
\solptb^{(1)} & = \volterra^\alpha \solptb^{(0)} \\
\solptb^{(2)} & = \volterra^\alpha \solptb^{(1)} \\
\solptb^{(3)} & = \volterra^\alpha \solptb^{(2)} \\
& \;\;\vdots
\end{align*}
we get a sequence of functions that converges in $\singexp{\tau_\alpha}{\Lambda}(\Omega_\alpha)$ to a solution.

\textcolor{orange}{[\ldots]}

%%Let's recall some notation from the proof. For convenience, we let $p = P(-\zeta)$ and $q = Q(-\zeta)$.

%%For convenience, let $p = P(-\zeta_\alpha)$ and $q = Q(-\zeta_\alpha)$. In \cite{reg-sing-volterra}, we observed that the Volterra operator $\hardpart^\alpha$ with kernel
%%Let $\hardpart^\alpha$ be the Volterra operator with kernel
%%\[ \hardker^\alpha(a,a') = -\frac{q(a')}{p(a)} \]
%%and let $\softpart^\alpha$ be the Volterra operator with kernel
%%\[ \softker^\alpha(a,a') = -\frac{k_R(a,a')}{p(a)}. \]

%%For convenience, let $p = P(-\zeta)$ and $q = Q(-\zeta)$.

%%As we did in the proof of Theorem~\ref{thm:sing-soln} from \cite{reg-sing-volterra}, let

%%\[ \hardker^\alpha(a,a') = -\frac{q(a')}{p(a)}, \]

%%\[ k_R(a,a')=\sum_{j=0}^\infty \frac{R_{j}}{j!} \, \big(\zeta(a)-\zeta(a')\big)^{j+1} . \]

Since $p$ has a simple root at $\zeta = \alpha$, the prototypical part $\hardpart^\alpha$ sends $\C\{\zeta_\alpha\}$ to itself. In fact, for any real number $\sigma$ that's not a negative integer, $\hardpart^\alpha$ maps $\zeta^\sigma \C\{\zeta_\alpha\}$ to itself. Under the same condition on $\sigma$, the operator $R(\partial^{-1}_{\zeta, \alpha})$ is well-defined as a map from $\zeta_\alpha^\sigma \C\{\zeta_\alpha\}$ to itself,\footnote{This is easiest to see from the formal point of view. Multiplication by $R(\zeta)$ sends convergent series to convergent series, and $\partial^{-1}_{\zeta, \alpha}$ acts like multiplication by $\zeta$ followed by the map $\zeta^\rho \mapsto \tfrac{1}{\Gamma(\rho+1)} \zeta^\rho$. A convergent series stays convergent under any operation that leaves its coefficients the same or smaller. \textcolor{orange}{[Discuss convergence of the operator series from the analytic point of view?]}.} so the perturbation can be seen as a map $\softpart^\alpha \maps \zeta_\alpha^\sigma \C\{\zeta_\alpha\} \to \zeta_\alpha^{\sigma + 1} \C\{\zeta_\alpha\}$.

\textcolor{orange}{[\ldots]}

\end{proof}
\begin{lemma}\label{lem:formal-general-volterra}
The equation $\hat{\mathcal{P}}_\alpha \series{\psi}_\alpha = 0$ has a unique formal solution $\series{\psi}_\alpha$ in the affine subspace
\[ \frac{\zeta_\alpha^{\tau_\alpha-1}}{\Gamma(\tau_\alpha)} + \zeta_\alpha^{\tau_\alpha} \C\llbracket \zeta_\alpha \rrbracket \]
of the space $\zeta_\alpha^{\tau_\alpha - 1} \C\llbracket \zeta_\alpha \rrbracket$.
\end{lemma}
\begin{proof}
\textcolor{orange}{[Argument of Loday-Richaud\ldots]}
\end{proof}
\begin{proof}
Let $\hat{\mathcal{P}}_\alpha$ be the Volterra operator defined in Section~4.5 of \cite{reg-sing-volterra}. Take any holomorphic function $\phi$ on $\Omega_\alpha$ with a well-defined Laplace transform $\Phi = \laplace_{\zeta,\alpha}^{\theta} \phi$ \textcolor{magenta}{[choose $\theta$]}. Lemma~2 of \cite{reg-sing-volterra} shows that $\hat{\mathcal{P}}_\alpha \phi = 0$ if and only if $\mathcal{P}\Phi = 0$ \textcolor{magenta}{[the lemma only states one direction; change it before publication to state both directions]}.

As a consequence of Theorem~\ref{thm:sing-soln}, the equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace
\[ \frac{\zeta^{\tau_\alpha-1}}{\Gamma(\tau_\alpha)} + \singexpalg{\tau_\alpha}(\Omega_\alpha) \]
of the space $\singexpalg{\tau_\alpha-1}(\Omega_\alpha)$. The same is true on any smaller sector created by shaving a sector off each edge of $\Omega_\alpha$. It follows, by the results of Section~\ref{sec:reg-decay} \textcolor{magenta}{[the domain $\Omega_\alpha$ needs to be a sector for this]}, that the equation $\mathcal{P}\Psi_\alpha = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace
\[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \]
of the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$.
